Untitled Draft

### 2023-01-24 doc/manuscript.Rmd
make manuscript complete

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "..")
setwd("..")
source("R/utils.R")
source("R/model_builder_RQ1.R")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "..")
#setwd("..")
source("R/utils.R")
source("R/model_builder_RQ1.R")
```
